Paper 2: Vitamin D

### 2017-09-23 doc/vitaminD.Rmd
replaced gee table code with function

gee_vitd_baseline %>% 
  dplyr::filter(!term == "(Intercept)") %>% 
  dplyr::mutate(p = round(p.value, 2),
    p = ifelse(p == "0", "<0.001", p),
    estCI = paste0(round(estimate, 2), " (",
                               round(conf.low, 2), ", ",
                               round(conf.high, 2), ")")) %>% 
  dplyr::select(Yterms, Xterms, term, estCI, p) %>% 
  # tidyr::spread(Yterms, estCI) %>%
  pander::pander()

>>>>

gee_vitd_baseline %>% 
  gee_results_table() %>% 
  # tidyr::spread(Yterms, estCI) %>%
  pander::pander()
